The SMT Competition 2015--2018

### 2019-08-16 2018/report/SMT-COMP.tex
Delete trailing whitespace
permitted -> allowed
lacking -> inadequate

Around the initial solver deadline, the organizers also aim to publish
the latest version of the competition tools, and---in collaboration
with the SMT-LIB maintainers---to release a new version of the SMT
Library (see Section~\ref{sec:smtlib}).  SMT-LIB releases were made on
June~1 in 2015, on May~23 in 2016, on June~5 in 2017, and on May~20 in
2018.  Anyone may submit new benchmarks to the SMT Library, and
competitors are permitted to tune their solvers accordingly.
Therefore all benchmarks eligible for the competition must be released
at least some time before the final solver submission deadline.  To
give the SMT-LIB maintainers sufficient time for curation, the
deadline for new benchmark contributions has usually been about four
to six weeks before the initial solver deadline, typically in April or
early May.

@@

\paragraph{Tracks.}
The \emph{\maintrack}, which
has been a staple of the competition since its
inception in 2005, features non-incremental benchmarks.  The
\emph{\apptrack}, which has been part of the competition since
2011~\cite{BDdMOS13}, features incremental benchmarks.  These
benchmarks are passed to each solver one command at a time by a trace
executor, which waits for the solver's response before passing the
next benchmark command (to prevent look-ahead behavior).  The
\emph{\ucoretrack} uses \maintrack benchmarks that are known to
be unsatisfiable, and solvers are evaluated on their ability to find
small unsatisfiable cores (i.e., a small but still unsatisfiable
subset of the benchmark's assertions).  The \ucoretrack had first
been part of the competition in 2012~\cite{CGBD12}, but was then
discontinued partly because of the competition's move to StarExec and
lacking tool support.  It was re-introduced as an experimental track
in 2016, and has been a regular competition track again since~2017.

@@

\paragraph{Eligible Benchmarks.}
Some benchmarks typically have to be
excluded for syntactic reasons: in 2015 and 2016, 11,966 benchmarks
were excluded because they contained partial or underspecified
operations (e.g., bit-vector division) whose precise semantics were
being debated at the time.  Additionally in~2016, one benchmark was
excluded because it contained incorrect status information.  In~2017,
1,104 benchmarks were excluded because their logic had been classified
incorrectly, and 8~benchmarks were excluded because of incorrect or
missing status information.  Moreover, divisions containing datatypes
({DT})---which were new in~2017---were excluded from the Unsat-Core
track because of lacking tool support.  In~2018, 3,603~benchmarks were
excluded because they contained named terms (a feature of the SMT-LIB
language that is not permitted in competition benchmarks), and
5~benchmarks were excluded because of missing status information.

>>>>

Around the initial solver deadline, the organizers also aim to publish
the latest version of the competition tools, and---in collaboration
with the SMT-LIB maintainers---to release a new version of the SMT
Library (see Section~\ref{sec:smtlib}).  SMT-LIB releases were made on
June~1 in 2015, on May~23 in 2016, on June~5 in 2017, and on May~20 in
2018.  Anyone may submit new benchmarks to the SMT Library, and
competitors are allowed to tune their solvers accordingly.
Therefore all benchmarks eligible for the competition must be released
at least some time before the final solver submission deadline.  To
give the SMT-LIB maintainers sufficient time for curation, the
deadline for new benchmark contributions has usually been about four
to six weeks before the initial solver deadline, typically in April or
early May.

@@

\paragraph{Tracks.}
The \emph{\maintrack}, which
has been a staple of the competition since its
inception in 2005, features non-incremental benchmarks.  The
\emph{\apptrack}, which has been part of the competition since
2011~\cite{BDdMOS13}, features incremental benchmarks.  These
benchmarks are passed to each solver one command at a time by a trace
executor, which waits for the solver's response before passing the
next benchmark command (to prevent look-ahead behavior).  The
\emph{\ucoretrack} uses \maintrack benchmarks that are known to
be unsatisfiable, and solvers are evaluated on their ability to find
small unsatisfiable cores (i.e., a small but still unsatisfiable
subset of the benchmark's assertions).  The \ucoretrack had first
been part of the competition in 2012~\cite{CGBD12}, but was then
discontinued partly because of the competition's move to StarExec and
inadequate tool support.  It was re-introduced as an experimental track
in 2016, and has been a regular competition track again since~2017.

@@

\paragraph{Eligible Benchmarks.}
Some benchmarks typically have to be
excluded for syntactic reasons: in 2015 and 2016, 11,966 benchmarks
were excluded because they contained partial or underspecified
operations (e.g., bit-vector division) whose precise semantics were
being debated at the time.  Additionally in~2016, one benchmark was
excluded because it contained incorrect status information.  In~2017,
1,104 benchmarks were excluded because their logic had been classified
incorrectly, and 8~benchmarks were excluded because of incorrect or
missing status information.  Moreover, divisions containing datatypes
({DT})---which were new in~2017---were excluded from the Unsat-Core
track because of inadequate tool support.  In~2018, 3,603~benchmarks were
excluded because they contained named terms (a feature of the SMT-LIB
language that is not permitted in competition benchmarks), and
5~benchmarks were excluded because of missing status information.
